FFT based convolution

### 2010-03-10 article/Article.tex
article continued
Ignore-this: 3cb26f566f0ce5f1a6ab5a859d1c8dae

darcs-hash:20100310002103-2fc9d-2de7876faf00dd5e223363042031a1eaf6e4c808.gz

% 
% NOTE: This is the last number of the "handle" URL that 
% The Insight Journal assigns to your paper as part of the
% submission process. Please replace the number "1338" with
% the actual handle number that you get assigned.
%
\newcommand{\IJhandlerIDnumber}{}

@@

This paper provides such a filter, as well as a detailed description of the implementation
choices and a comparison with the "simple" itk::ConvolutionImageFilter.

>>>>

% 
% NOTE: This is the last number of the "handle" URL that 
% The Insight Journal assigns to your paper as part of the
% submission process. Please replace the number "1338" with
% the actual handle number that you get assigned.
%
\newcommand{\IJhandlerIDnumber}{3154}

@@

This paper provides such a filter, as well as a detailed description of the implementation
choices and a performance comparison with the "simple" itk::ConvolutionImageFilter.
